---
title: "Iteration & Listcols"
author: "Alison Elgass"
date: "10/29/2019"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)

set.seed(1)
```

# Lists and things
Lists allow you to combine variables of different types  
(vectors limited to a single data class)
```{r}
vec_numeric = 5:8
vec_char = c("My", "name", "is", "Jeff")
vec_logical = c(TRUE, TRUE, TRUE, FALSE)
```

```{r}
l = list(vec_numeric = 5:8,
         mat         = matrix(1:8, 2, 4),
         vec_logical = c(TRUE, FALSE),
         summary     = summary(rnorm(1000)))

#index like normal
l$mat
l$vec_numeric
l[[1]]
l[[1]][1:3]
```

```{r}
df = list(
  a = rnorm(20, 3, 1),
  b = rnorm(20, 0, 5),
  c = rnorm(20, 10, .2),
  d = rnorm(20, -3, 1)
)
```

...Remember our friendly function we wrote
```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```

Try it on each element of list
```{r}
mean_and_sd(df[[1]])
mean_and_sd(df[[2]])
mean_and_sd(df[[3]])
mean_and_sd(df[[4]])
```

## For loops

Let's do the mean/sd function 4 times  
So basically we're doing the above code on the variable df by pre-defining an output variable then using a for loop
```{r}
#create an empty list of 4........................
output = vector("list", length = 4)
#.................................................

#now use a loop
for (i in 1:4) {
  output[[i]] = mean_and_sd(df[[i]]) 
}

output #display result
```

## Using Map
map (from purr package within tidyverse) allows us to do exactly what the above for loop does in a clearer way  

"The first argument to map is the vector/list/data frame we want to iterate over, and the second argument is the function we want to apply to each element"
```{r}
output = map(df, mean_and_sd)
output  #display it

output_median = map(df, median) #a different (built-in) fxn
```

### Map Variants
these alter the structure of output variable
```{r}
output = map_dbl(df, median, .id = "input") #vector
output = map_dfr(df, mean_and_sd, .id = "input")
output = map2(.x = input_1, .y = input_2, ~func(arg_1 = .x, arg_2 = .y))

```

# Napoleon Dynamite Example
Start with the function we wrote before
```{r}
read_page_reviews = function(url) {
  
  h = read_html(url)
  
  title = h %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  stars = h %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("\\d") %>%
    as.numeric()
  
  text = h %>%
    html_nodes(".review-data:nth-child(5)") %>%
    html_text()
  
  data_frame(title, stars, text)
}
```

So let's try to do this with this data
```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)
```

Using a for loop or a map statement
```{r}
#1. pre-define output 
output = vector("list", 5)

#2. for loop to fill output
for (i in 1:5) {
  output[[i]] = read_page_reviews(vec_urls[[i]])
}

#3. now bind together into a dataframe
dynamite_reviews = bind_rows(output)


#OR... we can just use a map statement!
dynamite_reviews = map_df(vec_urls, read_page_reviews)
```

# Weather Example
```{r}
weather = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2016-01-01",
    date_max = "2016-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

### Nesting
Since we have only 3 locations/station id's, let's separate data into 3 rows (each for 1 location) which each has a whole dataset (the rest of the columns)
```{r}
weather_nest = 
  nest(weather, data = date:tmin)

weather_nest #here is the nested dataset

#unnest(weather_nest, cols = data) #can reverse
```

We treat weather_nest like any other variable
```{r}
pull(weather_nest, name) #a character column
weather_nest %>% pull(name) #same thing

weather_nest %>% pull(data) #a list column, 3 parts
all_data = pull(weather_nest, data)
```

Now let's look at just the central park data
```{r}
central_park_df = weather_nest$data[[1]]
```

## Operations on list columns
"Suppose we want to fit the simple linear regression relating tmax to tmin for each station-specific data frame. First I’ll write a quick function that takes a data frame as the sole argument to fit this model"
```{r}
#linear regression function on a df
weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}

#test it on one dataframe
weather_lm(central_park_df)
```

Now use for loop or map to apply to all pieces of our list
```{r}
map(weather_nest$data, weather_lm)
```

But let's add a column to weather_nest with the linear regression output, using mutate
```{r}
weather_nest %>% 
  mutate(
    lin_models = map(data, weather_lm)
    #in map we iterate over "data" column of weather_nest
    #doing the weather_lm function
  )

#let's view new data for Central Park (column 3, list 1)
view(weather_nest[[3]][[1]])
```

