---
title: "Writing Functions"
author: "Alison Elgass"
date: "10/24/2019"
output: github_document
---
```{r}
library(tidyverse)
library(rvest)
set.seed(1)
```

How to calculate a z-score (by hand)
```{r}
aaa = rnorm(25, mean = 5, sd = 3)
(x - mean(x)) / sd(x)
```

# Our first function: z-scores
Let's write a function for z-scores
```{r}
z_scores = function(x) {
  
  z = (x - mean(x)) / sd(x)
  z   #this is the output
  
}
```
 
Try out the funciton
```{r}
z_scores(aaa)
z_scores(3) #outputs NA
z_scores("my name is Alison") #error
```

Now add conditions in case of wrong input
```{r}
z_scores_new = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  z = mean(x) / sd(x)
  
  z  #output
}
```

```{r}
```{r}
z_scores_new(aaa)
z_scores_new(3)
z_scores_new("my name is Alison")
```

## Two outputs, mean & sd
```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  #output as either a list or a tibble
  list(mean = mean_x, 
       sd = sd_x)
  
  tibble(
    mean = mean_x, 
    sd = sd_x)
}
```

```{r}
mean_and_sd(aaa)
```


# Multiple Inputs, linear regression

Linear regression by hand
```{r}
sim_data = tibble(
  x = rnorm(30, mean = 1, sd = 1),
  y = 2 + 3 * x + rnorm(30, 0, 1)
)

ls_fit = lm(y ~ x, data = sim_data)
  
beta0_hat = coef(ls_fit)[1]
beta1_hat = coef(ls_fit)[2]
```

Now a function for LR!
```{r}
sim_regression = function(n, beta0, beta1) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 1, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 1)
  )
  
  ls_fit = lm(y ~ x, data = sim_data)
  
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
  )
}
```

```{r}
sim_regression(30, 2, 3)
sim_regression(n = 30, beta0 = 2, beta1 = 3) #same
```


# Function to scrape web for reviews
```{r}
read_page_reviews = function(url) {
  
  h = read_html(url)
  
  review_titles = h %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  review_stars = h %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("\\d") %>%
    as.numeric()
  
  review_text = h %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()
  
  #outputs these 3 variables as a tibble
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}
```

```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
read_page_reviews(url_base)
```




